Automated Synthesis of State-Space Digital Controllers

### 2016-11-16 cav2017/cav2017.tex
generalised CEGIS + related work on CEGIS

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}

@@

\begin{thebibliography}{4}

\bibitem{jour} Smith, T.F., Waterman, M.S.: Identification of Common Molecular
Subsequences. J. Mol. Biol. 147, 195--197 (1981)

\end{thebibliography}

>>>>

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{framed}
\usepackage{listings}

\usetikzlibrary{positioning, arrows, automata, shapes}

\newcommand{\todo}[1]{{\color{red} TODO: #1}}

@@

\section{Counter-Example Guided Inductive Synthesis with solution generalisation}

\begin{figure}
\centering
\hspace*{-1cm}
\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=1cm, column sep=1.5cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \& ;\\
   \node[fill=yellow!20,align=center] (synth) {{\sc inductive}\\{\sc generalisation}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dashed,
	minimum width=7cm,
	minimum height=.8cm,
	label={\sc Validation oracles},] (verif) {};
   \node[fill=yellow!20] (verif1) at ([xshift=-2.1cm]verif.center) {{\sc Validate}};
   \node[fill=yellow!20,align=center] (verif2) at ([xshift=1.9cm]verif.center) {{\sc validate general}};
   } 
   \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}};\\
   %% \node[fill=yellow!20] (verif) {{\sc ~~~~~~Uncertainty~~~~~~}};
   %% \&
   %% \node[fill=yellow!20] (verif2) {{\sc ~~~~~~Precision~~~~~~~}};\\
   \& \\
   \& \\
   \node (gp) {Program Search};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node (bmc) at ([xshift=-2.1cm]aux.center) {SAT/SMT Solver};
   \node (fp)  at ([xshift=1.9cm]aux.center) {SAT/SMT Solver};
   }   
    \\
  };

   \path
    ([yshift=2em]synth.east) edge node[xshift=-0.7em] {Candidate} ([yshift=2em]verif1.west)
    ([yshift=-2em]verif1.west) edge node[xshift=-0.7em] {New input} ([yshift=-2em]synth.east)
    (verif1) edge node {Generalise} (verif2)
    ([xshift=5em]verif1.south) edge node[align=center] {Candidate} ([xshift=5em]bmc.north)
    ([xshift=5em]verif2.south) edge node[align=center] {Candidate} ([xshift=5em]fp.north)
    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\Model} ([xshift=-5em]verif1.south)
    ([xshift=-5em]fp.north) edge node[align=center]  {UNSAT/\\Model} ([xshift=-5em]verif2.south)
    (verif2) edge node {} (done)
    ([xshift=5em]synth.south) edge node[align=center] {{\sc Inputs}} ([xshift=5em]gp.north)
    ([xshift=-5em]gp.north) edge node[align=center] {No solution/\\Candidate} ([xshift=-5em]synth.south)
    (aux1) edge (synth.north);
   \path[-]
   (verif2.north) edge node[align=center] {} ([xshift=6.5cm]aux2)
   ([xshift=6.5cm]aux2) edge node[align=center] {Increase parameters} (aux1);

\end{tikzpicture}
\caption{The CEGIS loop with solution generalisation\label{fig:CEGIS-multiple-verif}}
\end{figure}

\section{Related works}

\paragraph{CEGIS}

Program synthesis is the problem of computing correct-by-design programs
from high-level specifications, and algorithms for this problem have made
substantial progress in recent years.  One such
approach~\cite{itzhaky2010simple} inductively synthesizes invariants to
generate the desired programs.

Program synthesisers are an ideal fit for synthesis of parametric
controllers since the semantics of programs capture effects such as FWL
precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS
for the synthesis of switching controllers for stabilizing continuous-time
plants with polynomial dynamics.  The work extends to its application on
affine systems, finding its major challenge in the hardness of solving
linear arithmetic with the state-of-the-art SMT solvers.  Since this
approach uses switching states instead of linear dynamics in the digital
controller, it entirely circumvents the FWL problem.  It is also not
suitable for the kind of control we seek to synthesize.  We require a
combination of a synthesis engine with a control verification tool that
addresses the challenges presented here in the form of FWL effects and
stability measures for LTI SISO controllers.  We take the former
from~\cite{DBLP:conf/lpar/DavidKL15} and the latter from~\cite{daes20161}
while enhancing the procedure by evaluating the quantization effects of the
Hardware interfaces (ADC/DAC) to obtain an accurate discrete-time FWL
representation of the continuous dynamics.

\bibliographystyle{abbrv}
\bibliography{paper}  
%\begin{thebibliography}{4}
%\end{thebibliography}
